### 2014-07-24 MS.tex
legends for supp figures

\section*{Supp. mat.}

\textbf{\texttt{Supporting_Information_S1.nex}}: \textbf{Genus}. MCC Nymphalidae tree from
Reference 10.

\textbf{\texttt{Supporting_Information_S2.R}}: \textbf{Run_medusa_on_mct}. Run MEDUSA on
MCC tree from Reference 10.

@@

\textbf{\texttt{Supporting_Information_S10.R}}:
Run MEDUSA on MCC tree from the 1000 random trees selected from the
posterior distribution.

\textbf{\texttt{Supporting_Information_S11.txt}}:
Summary results from a MEDUSA run on the MCC tree from the 1000 random
trees selected from the posterior distribution.

\textbf{\texttt{Supporting_Information_S12.pdf}}:
Figure for MEDUSA run on MCC tree from random 1000 trees.

\textbf{\texttt{Supporting_Information_S13.txt}}:
Summary results from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution.

\textbf{\texttt{Supporting_Information_S14.pdf}}:
Probability of nodes with estimated rates from a MultiMEDUSA run on the
1000 random trees selected from the posterior distribution.

\textbf{\texttt{Supporting_Information_S15.csv}}: Hostplants of
Nymphalidae butterflies recorded from the literature.

\textbf{\texttt{Supporting_Information_S16.csv}}:
References for hostplants data.

\textbf{\texttt{Supporting_Information_S17.csv}}: Data matrix with
character states for hosplant use.

\textbf{\texttt{Supporting_Information_S18.R}}: R code for running the
BiSSE analysis.

\textbf{\texttt{Supporting_Information_S19.csv}}: Raw results for
the BiSSE analysis.

\textbf{\texttt{Supporting_Information_S20.csv}}: Raw results for
the combined BiSSE analysis.

>>>>

\section*{Supporting Information}
\texttt{Figure S1.} Boxplot of speciation (lambda) and extinction (mu)
values for the 95\% credibility intervals of values estimated by BiSSE
analysis of diversification due to feeding on Solanaceae plants.

\texttt{Figure S2.} BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders (\$lambda\$1, r1).

\texttt{Figure S3.} Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution.

\texttt{Figure S4.} Boxplot of speciation and extinction values for the
95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.

\texttt{Figure S5.} BiSSE analysis of diversification of nymphalids due
to feeding on Apocynaceae hostplants. Speciation and net diversification
rates are similar.

\textbf{\texttt{Supporting\_Information\_S1.nex}}: \textbf{Genus}. MCC Nymphalidae tree from
Reference 10.

\textbf{\texttt{Supporting\_Information\_S2.R}}: \textbf{Run medusa on mct}. Run MEDUSA on
MCC tree from Reference 10.

@@

\textbf{\texttt{Supporting\_Information\_S10.R}}:
Run MEDUSA on MCC tree from the 1000 random trees selected from the
posterior distribution.

\textbf{\texttt{Supporting\_Information\_S11.txt}}:
Summary results from a MEDUSA run on the MCC tree from the 1000 random
trees selected from the posterior distribution.

\textbf{\texttt{Supporting\_Information\_S12.pdf}}:
Figure for MEDUSA run on MCC tree from random 1000 trees.

\textbf{\texttt{Supporting\_Information\_S13.txt}}:
Summary results from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution.

\textbf{\texttt{Supporting\_Information\_S14.pdf}}:
Probability of nodes with estimated rates from a MultiMEDUSA run on the
1000 random trees selected from the posterior distribution.

\textbf{\texttt{Supporting\_Information\_S15.csv}}: Hostplants of
Nymphalidae butterflies recorded from the literature.

\textbf{\texttt{Supporting\_Information\_S16.csv}}:
References for hostplants data.

\textbf{\texttt{Supporting\_Information\_S17.csv}}: Data matrix with
character states for hosplant use.

\textbf{\texttt{Supporting\_Information\_S18.R}}: R code for running the
BiSSE analysis.

\textbf{\texttt{Supporting\_Information\_S19.csv}}: Raw results for
the BiSSE analysis.

\textbf{\texttt{Supporting\_Information\_S20.csv}}: Raw results for
the combined BiSSE analysis.
